Supplementary Content

### 2022-03-30 experiments/2_supplement/supplement.Rmd
Next step Graphs Appendix

```{r include = FALSE, echo = FALSE}
knitr::opts_chunk$set(include = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      cache = TRUE)
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
```

@@

dd %>%
  filter(State_variable %in% c("O", "SR", "SO"),
         direction == "up",
         a_O < as.numeric(aO_flip_sim2),
         a_O > -3.5) %>%
  ggplot(aes(x = log10(Quantity_sim1),
                 y = log10(Quantity_sim2),
                 col = a_O )) +
  geom_point(lwd = 3) +
  geom_path() +
  scale_color_gradient(low = "yellow", high = "red", na.value = NA,
                       breaks = labs,
                       labels = labs) +
  #coord_trans(x = "log10", y = "log10") +
  facet_wrap( ~ State_variable, scales = "free") +
  geom_abline(intercept = 0, slope = 1) +
  xlab("log10(concentration) (µM)\nLow PB diversity") +
  ylab("log10(concentration) (µM)\nHigh PB diversity") +
  labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
  theme_bw() +
  theme(legend.position="top")

>>>>

```{r include = FALSE, echo = FALSE}
knitr::opts_chunk$set(include = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE)
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
p <- plot_dynamics(sim_res_novar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[4]] <- p[[4]] + 
  xlab("time(h)") + 
  ylab(expression(log[10](concentration)(µM))) + 
  labs(colour = "substrate")

p
#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
```

@@

dd %>%
  filter(State_variable %in% c("O", "SR", "SO"),
         direction == "up",
         a_O < as.numeric(aO_flip_sim2),
         a_O > -3.5) %>%
  ggplot(aes(x = log10(Quantity_sim1),
                 y = log10(Quantity_sim2),
                 col = a_O )) +
  geom_point(lwd = 3) +
  geom_path() +
  scale_color_gradient(low = "yellow", high = "red", na.value = NA,
                       breaks = labs,
                       labels = labs) +
  #coord_trans(x = "log10", y = "log10") +
  facet_wrap( ~ State_variable, scales = "free") +
  geom_abline(intercept = 0, slope = 1) +
  xlab(expression(atop(log[10](concentration)~(µM), Low~PB~diversity))) +
  ylab(expression(atop(log[10](concentration)~(µM),High~PB~diversity))) +
  labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
  theme_bw() +
  theme(legend.position="top")
```
